---
title: "Final Project"
author: "Max Vumbaca"
date: "October 19, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE, message=FALSE}
library(tidyverse)
library(readxl)
cambridge <-   read_csv("Cambridge_Homeless_Point-in-Time_Count_data__2012-2018.csv")
homeless <- read_excel("2007-2017-PIT-Counts-by-CoC.XLSX")
```

This dataset contains the data collected by Cambridge government regarding homelessness in the city from 2012-2017. Every year a count of individuals experiencing homelessness is taken on a single night in January. Demographic information about the individuals counted is also collected but is recorded in aggregate for the given year.

```{r echo=FALSE}
cambridge %>%
  nrow()
```

Cambridge sends its annual homelessness data to the U.S. Department of Housing and Urban Development. This second dataset includes data from all cities that submitted to HUD in 2017. It will serve as another potential option if the first one proves too narrow.

```{r echo=FALSE}
homeless %>%
  nrow()
```
